### 2011-11-03 Text/introduction.tex
Added triple results.

\section{Two unit cells results}
As far as one needs to restore the continuous picture one needs to make a simulation of a few
cells. This section provides results for two units. The results are summarized in Table
\ref{table:two_units}. The results for two sections are presented in Fig. \ref{fig:results:double}.
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/steady_double_overall.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_double_first.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/steady_double_second.eps}
\caption{Overall mass transfer coefficient (top left), first part (top
right), second part (bottom left).\label{fig:results:double}}
\end{figure}
\begin{table}[htb!]
\begin{tabularx}{\textwidth}{|X|X|X|}
$0.7392$&$1.0564$&$0.4220$\\
$1.8993$&$2.8301$&$0.9684$\\
$3.3925$&$4.7522$&$2.0328$\\
$3.7870$&$4.5615$&$3.0125$\\
\end{tabularx}
\caption{Simulation results. \label{table:two_units}}
\end{table}

>>>>

\section{Two unit cells results}
As far as one needs to restore the continuous picture one needs to make a simulation of a few
cells. This section provides results for two units. The results are summarized in Table
\ref{table:two_units}. The results for two sections are presented in Fig. \ref{fig:results:double}.
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/steady_double_overall.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_double_first.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/steady_double_second.eps}
\caption{Overall mass transfer coefficient (top left), first part (top
right), second part (bottom left).\label{fig:results:double}}
\end{figure}
\begin{table}[htb!]
\begin{tabularx}{\textwidth}{|X|X|X|}
$0.7392$&$1.0564$&$0.4220$\\
$1.8993$&$2.8301$&$0.9684$\\
$3.3925$&$4.7522$&$2.0328$\\
$3.7870$&$4.5615$&$3.0125$\\
\end{tabularx}
\caption{Simulation results for two units. \label{table:two_units}}
\end{table}

\section{Three unit cells results}
Three unit cells results are subdivided into three cells. We calculate the mass transfer
coefficients over the each cell, Fig. \ref{fig:results:triple}. The averaged coefficients  after
$3,300,000$ time steps are represented in Table. \ref{table:three_units}. The most important thing
is to look at the third column of the Table \ref{table:three_units} or for at the Fig. \ref{fig:re} 
\begin{table}[htb!]
\begin{tabularx}{\textwidth}{|X|X|X|X|}
0.4928&1.0564&2.8472e-05&0.4219\\
1.2662&2.8301&0.0146&0.9537\\
2.3110&4.7532&1.0665&1.1133
\end{tabularx}
\caption{Simulation results for three units.\label{table:three_units}}
\end{table}
\begin{figure}[htb!]
\includegraphics[width=0.5\textwidth]{Figures/steady_triple_overall.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_triple_first.eps}\\
\includegraphics[width=0.5\textwidth]{Figures/steady_triple_second.eps}
\includegraphics[width=0.5\textwidth]{Figures/steady_triple_third.eps}\\
\caption{The mass transfer coefficient over time in different locations: overall mass transfer
coefficient (top left), first part (top right), second part (bottom left), third part (bottom
right). \label{fig:results:triple}}
\end{figure}
